Blueprint for efficient nuclear spin characterization in color center

### 2024-01-31 article.tex
ploting the ellipse plis workin on the refs

\begin{abstract}
Nuclear spins in solids offer a promising avenue for developing scalable quantum hardware. Leveraging nearby single-color centers, these spins can be efficiently addressed at the single-site level through spin resonance.
However, characterising individual nuclear spin is quite cumbersome since the utility of characterisation protocols may differ depending on the strength of the hyperfine coupling, necessitating tailored characterization protocols.
While modified electron spin Hahn echoes like CPMG and XY8 pulse sequences are commonly employed, they encounter significant limitations in scenarios involving spin-1/2 systems, strongly coupled spins, or nuclear spin baths comprising distinct isotopes.
Here, we present a more straightforward approach for determining the hyperfine interactions among each nuclear and the electron spin. 
This method holds promise across diverse platforms, including emerging S=1/2 group IV defects in diamond (e.g., SiV, GeV, SnV, PbV) or silicon vacancies in silicon carbide. 
We provide a theoretical framework and adapt it for use with color centers exhibiting various spins. Through simulations conducted on nuclear spin clusters, we evaluate different protocols and compare their performance using the Fisher information matrix.
\end{abstract}

@@

Traditionally, nuclear spin characterization is accomplished through Optically Detected Magnetic Resonance (ODMR) \cite{Dreau, Neumann, Eriks}, but the spectroscopic resolution is constrained by the $1/T_2^\ast$ of the electron spin. 

@@

Also, the protocols also can only be applied to electron spins with a specific spin multiplicity

@@

Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow access to the highest number of nuclear spins, as the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system. (see fig. \ref{fig:1}) \cite{Laraui, Vorobyov}.
In particular, we consider the following common examples of nuclear spin registers that are ubiquitous in applications. First, the NV-like case with S=1 and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied in the works of \cite{abobeih2019atomic, taminiau2012detection, Tam2014, Wrachtrup, before}.

@@

The third case (Fig. 1c) pertains to the S=1/2 scenario, where the lack of offset in the average evolution of the nuclear spin results in its dynamics weakly depending on Azz and only in the second order on $A_{zx}$ \cite{suckachev}.
Consequently, this leads to a limited ability to distinguish between multiple nuclear spins and, consequently, a lack of individual addressability of nuclear spins.

@@

In this work, we propose that a correlation-type sequence, based on five pulse ESEEM, could serve as a general framework as it holds promise for the reconstruction of the interactions in all of the aforementioned cases.

@@

In this work, we consider 23 nuclear spins characterized in paper \cite{abobeih2019atomic} as a realistic case.
\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported in  \cite{abobeih2019atomic} assuming the electron spin is a. spin 1 system b. spin 1/2 system. Simulated Fisher information matrix for the case of the electron spin c. spin 1 system d. spin 1/2 system.}
		\label{fig:3}
	\end{center}
\end{figure*}
In this work, we consider the 23-nuclear spin cluster characterized in paper \cite{abobeih2019atomic} as a realistic case for our comparison.
First, we apply this to the dynamical decoupling sequence and visualize the obtained results. Fig \ref{fig:3} compares the DD signal for the same nuclear spin register but different defects in diamond.
An intuitive description of the sensitivity of a sequence to the variation of hyperfine coupling could be estimated by considering the width and sensitivity of the position of the resonances.
First, we consider the case of an NV center in diamond. The width of a dip is $\delta \tau = \frac{A_{zx}}{\omega_L^2}$. Taking the derivative of the resonance time, we define the sensitivity of the longitudinal hyperfine coupling as follows, using Eq. \ref{eq:resonance} to simplify:
\begin{gather}
	\delta A_{zz} \equiv \frac{\delta \tau}{\abs{\frac{\partial \tau_p}{\partial A_{zz}}}} = \frac{2}{\tau_p} \frac{A_{zx}}{\omega_L} \ge \frac{4}{T_2^{HE}} \frac{A_{zx}}{\omega_L}
\end{gather}
If we assume typical values of $T_2^{HE} = 100$ $\mu$s and $\omega_L=500$ kHz, a weakly coupled nuclear spin $A_{zx}=5$ kHz can be distinguished from another weakly coupled nuclear spin with $\delta A_{zz} = 400$ Hz.
For $S=1/2$, such as group IV defects in diamond, the resonance times are sensitive to the second order of $A_{zx}$ and show no sensitivity to $A_{zz}$.
Hence, even at large $\tau$, the resonances related to nuclear spins will not be well separated.
We define the sensitivity for the spin one-half system as follows:
\begin{gather}
	\delta A_{zx} \equiv \frac{\delta \tau}{\abs{\frac{\partial \tau_k}{\partial A_{zx}}}} = \frac{4}{\tau_k} \ge \frac{8}{T_2^{HE}}
\end{gather}
Assuming typical values of $T_2^{HE} = 100$ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate and approximately 160 times worse than for $S=1$.

>>>>

\begin{abstract}
Nuclear spins in solids offer a promising avenue for developing scalable quantum hardware. Leveraging nearby single-color centers, these spins can be efficiently addressed at the single-site level through spin resonance.
However, characterising individual nuclear spin is quite cumbersome since the utility of characterisation protocols may differ depending on the strength of the hyperfine coupling, necessitating tailored characterization protocols.
While modified electron spin Hahn echoes like CPMG and XY8 pulse sequences are commonly employed, they encounter significant limitations in scenarios involving spin-1/2 systems, strongly coupled spins, or nuclear spin baths comprising distinct isotopes.
Here, we present a more straightforward approach for determining the hyperfine interactions among each nuclear and the electron spin. 
This method holds promise across diverse platforms, especially for emerging S=1/2 group IV defects in diamond (e.g., SiV, GeV, SnV, PbV) or silicon (T-centre). 
We provide a theoretical framework and adapt it for use with color-centers exhibiting various spins. Through simulations conducted on nuclear spin clusters, we evaluate different protocols and compare their performance using the Fisher information matrix.
\end{abstract}

@@

Traditionally, nuclear spin characterization is accomplished through Optically Detected Magnetic Resonance (ODMR) \cite{Dreau:2012aa,hesselmeier2023measuring}, but the spectroscopic resolution is constrained by the $1/T_2^\ast$ of the electron spin. 

@@

Also, the protocols also can only be applied to electron spins with a specific spin multiplicity.

@@

Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow access to the highest number of nuclear spins, as the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system. (see fig. \ref{fig:1}) \cite{laraoui2013high, vorobyov2022addressing}.
In particular, we consider the following common examples of nuclear spin registers that are ubiquitous in applications. First, the NV-like case with $S=1$ and weakly coupled nuclear spins, operating at high magnetic fields where $\gamma_n B \gg A_{zx}$ which has been extensively studied in the works of \cite{abobeih2019atomic, taminiau2012detection, Zhao:2014aa}.

@@

The third case (Fig. \ref{fig:1}c) pertains to the $S=1/2$ scenario, where the lack of offset in the average evolution of the nuclear spin results in its dynamics weakly depending on $A_{zz}$ and only the second order dependence on $A_{zx}$.
Consequently, this leads to a limited ability to distinguish between multiple nuclear spins and a lack of individual addressability of nuclear spins.

@@

While the double resonance methods \cite{Bradley:2019aa,zaiser2016enhancing} posses a large promise for nuclear spin spectroscopy, they require additional experimental hardware, and often are not available. 
Thus, in this work, we investigate the limits of electron spin driven schemes, in particular a correlation-type sequences, which could serve as a general framework and hold promise for the reconstruction of the interactions in all of the aforementioned cases.

@@

\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}
		\caption{Simulated DD signal with 64 $\pi$-pulses for the register reported in  \cite{abobeih2019atomic} assuming the electron spin is a. spin 1 system b. spin 1/2 system. Simulated Fisher information matrix for the case of the electron spin c. spin 1 system d. spin 1/2 system.}
		\label{fig:3}
	\end{center}
\end{figure*}
In this work, we consider the 23-nuclear spin cluster characterized in paper \cite{abobeih2019atomic} as a realistic case for our comparison.
First, we apply this to the dynamical decoupling sequence and visualize the obtained results. Fig \ref{fig:3} compares the DD signal for the same nuclear spin register but different defects in diamond.
An intuitive description of the sensitivity of a sequence to the variation of hyperfine coupling could be estimated by considering the width and sensitivity of the position of the resonances.
First, we consider the case of an NV center in diamond. The width of a dip is $\delta \tau = \frac{A_{zx}}{\omega_L^2}$. Taking the derivative of the resonance time, we define the sensitivity of the longitudinal hyperfine coupling as follows, using Eq. \ref{eq:resonance} to simplify:
\begin{gather}
	\delta A_{zz} \equiv \frac{\delta \tau}{\abs{\frac{\partial \tau_p}{\partial A_{zz}}}} = \frac{2}{\tau_p} \frac{A_{zx}}{\omega_L} \ge \frac{4}{T_2^{HE}} \frac{A_{zx}}{\omega_L}
\end{gather}
If we assume typical values of $T_2^{HE} = 100$ $\mu$s and $\omega_L=500$ kHz, a weakly coupled nuclear spin $A_{zx}=5$ kHz can be distinguished from another weakly coupled nuclear spin with $\delta A_{zz} = 400$ Hz.
For $S=1/2$, such as group IV defects in diamond, the resonance times are sensitive to the second order of $A_{zx}$ and show no sensitivity to $A_{zz}$.
Hence, even at large $\tau$, the resonances related to nuclear spins will not be well separated.
We define the sensitivity for the spin one-half system as follows:
\begin{gather}
	\delta A_{zx} \equiv \frac{\delta \tau}{\abs{\frac{\partial \tau_k}{\partial A_{zx}}}} = \frac{4}{\tau_k} \ge \frac{8}{T_2^{HE}}
\end{gather}
Assuming typical values of $T_2^{HE} = 100$ $\mu$s, a nuclear spin can be distinguished from another one if their transverse hyperfine coupling is separated by $\delta A_{zx} = 80$ kHz, which is quite inaccurate and approximately 160 times worse than for $S=1$.
